---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# tidygramr

`tidygramr` is a collection of utility functions based on the [tidytext](https://cran.r-project.org/package=tidytext) package. The goal of `tidygramr` is to clean text and to prepare tidy n-gram models. 

**License:** [MIT](https://opensource.org/licenses/MIT)

## Installation

You can install `tidygramr` from github using [devtools](https://cran.r-project.org/package=devtools):

```{r gh-installation, eval = FALSE}
library(devtools)
install_github("cldatascience/tidygramr")
```

## Examples

Here are some basic examples outlining how to create n-gram models from
Jane Austen's works (see 
[janeaustenr](https://cran.r-project.org/package=janeaustenr)).
These examples replicate examples in the book
[Tidy Text Mining with R](http://tidytextmining.com/ngrams.html), 
but make use of utility functions in `tidygramr` to obtain the same results.

Create n-gram models:

```{r example1, warning=FALSE}
library(janeaustenr)
library(tidygramr)
unigrams <- create_ngrams(austen_books(), "unigram")
bigrams <- create_ngrams(austen_books(), "bigram")
trigrams <- create_ngrams(austen_books(), "trigram")
```

Create a table of bigram frequencies (stop words removed):

```{r example2, warning=FALSE}
library(tidytext)
library(janeaustenr)
library(tidygramr)
bigrams <- create_ngrams(austen_books(), "bigram", stopwords=stop_words)
bigram_freqs <- count_ngrams(bigrams, doc_title="book")
head(bigram_freqs)
```

Calculate tf-idf of bigrams (stop words removed):

```{r example3, warning=FALSE}
library(tidytext)
library(janeaustenr)
library(tidygramr)
bigrams <- create_ngrams(austen_books(), "bigram", stopwords=stop_words)
bigram_tfidf <- create_tfidf(bigrams, doc_title="book")
head(bigram_tfidf)
```

For more information on tidy text mining, please see the excellent
[Tidy Text Mining with R](http://tidytextmining.com/ngrams.html).
